\LARGE \bf Matrix Multiplication-Driven Repulsive Fields for Manipulator Kinematic Obstacle Avoidance

### 2024-03-19 Articles/IROS/root.tex
managing references - part 1

While global motion planning techniques provide comprehensive solutions by examining the entire configuration space, they fall short in terms of smoothness and real-time application, making them less ideal for dynamic settings~\cite{vsvestka1997motion,lavalle1998rapidly, karaman2010incremental,kuffner2000rrt,gammell2015batch}. Conversely, local planning methods, particularly inverse kinematics and quadratic programming, offer prompt, smooth trajectories suitable for real-time operations. However, these methods are prone to fall into local minima due to their incremental planning approach~\cite{c29,c38,c21,c23}.

@@

The Artificial Potential Field (APF) concept introduced by Khatib~\cite{c33}, employs repulsive forces for obstacle deflection and attractive forces to guide towards targets, many modifications of the method have been proposed over the year, often trying to mitigate local minima~\cite{c40,c43,c45,c46,c47}. Some methods have further adapted APF for manipulator motion planning, incorporating elements such as numerical Jacobians to refine trajectory planning~\cite{c49,park2020trajectory}.

@@

\bibitem{IDEASLab2023}
IDEAS Lab, "Motion and Path Planning," presented at Purdue University, 2023. [Online]. Available: \url{https://ideas.cs.purdue.edu/research/robotics/planning/}. Accessed on: Jan. 9, 2024.

@@

\bibitem{c22} H. Toshani and M. Farrokhi, “Real-time inverse kinematics of redundant manipulators using neural networks and quadratic programming: A Lyapunov-based approach,” Robotics and Autonomous Systems, vol. 62, no. 6, pp. 766–781, Jun. 2014. doi: 10.1016/j.robot.2014.02.005.

@@

\bibitem{c23} Y. Zhang, S. S. Ge, and T. H. Lee, “A Unified Quadratic-Programming-Based Dynamical System Approach to Joint Torque Optimization of Physically Constrained Redundant Manipulators,” IEEE Trans. Syst., Man, Cybern. B, vol. 34, no. 5, pp. 2126–2132, Oct. 2004. doi: 10.1109/TSMCB.2004.830347.

@@

\bibitem{c40} J.-O. Kim and P. Khosla, “Real-Time Obstacle Avoidance Using Harmonic Potential Functions,” 1992. doi: 10.1109/70.143352.

@@

\bibitem{c46} A. H. Qureshi et al., “Adaptive Potential guided directional-RRT*,” in Proc. 2013 IEEE International Conference on Robotics and Biomimetics (ROBIO), Shenzhen, China, Dec. 2013, pp. 1887–1892. doi: 10.1109/ROBIO.2013.6739744.

@@

\bibitem{vsvestka1997motion} P. {\v{S}}vestka and M. H. Overmars, “Motion planning for carlike robots using a probabilistic learning approach,” The International Journal of Robotics Research, vol. 16, no. 2, pp. 119–143, 1997.

\bibitem{gammell2014informed} J. D. Gammell, S. S. Srinivasa, and T. D. Barfoot, “Informed RRT*: Optimal sampling-based path planning focused via direct sampling of an admissible ellipsoidal heuristic,” in Proc. of the 2014 IEEE/RSJ International Conference on Intelligent Robots and Systems, Chicago, IL, USA, Sep. 2014, pp. 2997–3004. doi: 10.1109/IROS.2014.6942976.

>>>>

While global motion planning techniques provide comprehensive solutions by examining the entire configuration space, they fall short in terms of smoothness and real-time application, making them less ideal for dynamic settings~\cite{lavalle1998rapidly, gammell2015batch, karaman2010incremental,kuffner2000rrt}. Conversely, local planning methods, particularly inverse kinematics~\cite{c29,c38} and quadratic programming~\cite{c21,c23}, offer prompt, smooth trajectories suitable for real-time operations. However, these methods are prone to fall into local minima due to their incremental planning approach.

@@

The Artificial Potential Field (APF) concept introduced by Khatib~\cite{c33}, employs repulsive forces for obstacle deflection and attractive forces to guide towards targets, many modifications of the method have been proposed over the year, often trying to mitigate local minima~\cite{c43,c45,c47,klancar2022robot}. Some methods have further adapted APF for manipulator motion planning, incorporating elements such as numerical Jacobians to refine trajectory planning~\cite{c49,park2020trajectory,baumgartner2023potential}.

@@

%\bibitem{vsvestka1997motion} P. {\v{S}}vestka and M. H. Overmars, “Motion planning for carlike robots using a probabilistic learning approach,” The International Journal of Robotics Research, vol. 16, no. 2, pp. 119–143, 1997.

@@

\bibitem{c23} H. Toshani and M. Farrokhi, “Real-time inverse kinematics of redundant manipulators using neural networks and quadratic programming: A Lyapunov-based approach,” Robotics and Autonomous Systems, vol. 62, no. 6, pp. 766–781, Jun. 2014. doi: 10.1016/j.robot.2014.02.005.

%\bibitem{c22} Y. Zhang, S. S. Ge, and T. H. Lee, “A Unified Quadratic-Programming-Based Dynamical System Approach to Joint Torque Optimization of Physically Constrained Redundant Manipulators,” IEEE Trans. Syst., Man, Cybern. B, vol. 34, no. 5, pp. 2126–2132, Oct. 2004. doi: 10.1109/TSMCB.2004.830347.

%\bibitem{c40} J.-O. Kim and P. Khosla, “Real-Time Obstacle Avoidance Using Harmonic Potential Functions,” 1992. doi: 10.1109/70.143352.

%\bibitem{c46} A. H. Qureshi et al., “Adaptive Potential guided directional-RRT*,” in Proc. 2013 IEEE International Conference on Robotics and Biomimetics (ROBIO), Shenzhen, China, Dec. 2013, pp. 1887–1892. doi: 10.1109/ROBIO.2013.6739744.

\bibitem{klancar2022robot}
G. Klančar, A. Zdešar, and M. Krishnan, “Robot Navigation Based on Potential Field and Gradient Obtained by Bilinear Interpolation and a Grid-Based Search,” Sensors, vol. 22, no. 9, art. no. 3295, pp. 1-24, 2022. doi: 10.3390/s22093295.

\bibitem{baumgartner2023potential}
J. Baumgartner, T. Petrič, and G. Klančar, “Potential Field Control of a Redundant Nonholonomic Mobile Manipulator with Corridor-Constrained Base Motion,” Machines, vol. 11, no. 2, art. no. 293, pp. 1-28, 2023. doi: 10.3390/machines11020293.

%\bibitem{gammell2014informed} J. D. Gammell, S. S. Srinivasa, and T. D. Barfoot, “Informed RRT*: Optimal sampling-based path planning focused via direct sampling of an admissible ellipsoidal heuristic,” in Proc. of the 2014 IEEE/RSJ International Conference on Intelligent Robots and Systems, Chicago, IL, USA, Sep. 2014, pp. 2997–3004. doi: 10.1109/IROS.2014.6942976.
%
%	
%\bibitem{IDEASLab2023}
%IDEAS Lab, "Motion and Path Planning," presented at Purdue University, 2023. [Online]. Available: \url{https://ideas.cs.purdue.edu/research/robotics/planning/}. Accessed on: Jan. 9, 2024.
%

@@

@@

@@

@@
